---
title: "Vasarely Tests"
author: "Alexandra Banach 649005"
date: "29 Juni 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/limes/Documents/Semester6/Bachelorarbeit/vasarely/R")
library("vasarely")
```

load testdata (without column X) and test plot function
```{r}
testdata <- as.data.frame(read.csv("testdata5"))
```
test grey value parameter with false input
```{r}
vasarely(testdata, testdata)
```
test data with more than two columns
```{r}
testdata3 <- as.data.frame(read.csv("testdata"))
vasarely(testdata3,blues9)
```
test data with less than two columns
```{r}
testdata4 <- as.data.frame(read.csv("testdata_new"))
testdata4$allel2 <- NULL
vasarely(testdata4, blues9)
```
test data with grey values
```{r}
vasarely(testdata,blues9)
vasarely(testdata)
```
test data with numbers
```{r}
 
a <- rep(c(1:10), each = 10)
b <- sample(c(1:10), 100, replace = TRUE)
data2 <- data.frame(a, b)
vasarely(data2)
```

official example

```{r }
a3 <- c(rep("A", each = 25), rep("B", each = 75))
a4 <- c(rep("A", each = 50), rep("B", each = 50))
data3 <- data.frame(a3, a4)
vasarely(data3)
```

Check if package was successfully installed
```{r}
"vasarely" %in% rownames(installed.packages())
```
Normal Marker, ten alleles
```{r}
letters <- c('A','B','C','D','E','F','G','H','I','J')
a1 <- sample(letters, 100, replace = TRUE)
a2 <- sample(letters, 100, replace = TRUE)
vasarely_data1 <- data.frame(a1,a2)
vasarely(vasarely_data1)
```
marker with null alleles
```{r}
a1 <- rep(letters, mal=10)
a2 <- rep(letters, mal=10)
a1 <- c(a1,sample(letters, 10, replace = TRUE))
a2 <- c(a2,sample(letters, 10, replace = TRUE))
vasarely_data2 <- data.frame(a1,a2)
vasarely(vasarely_data2)
```
adjacent alleles
```{r}

```
AB-deficit (uncorrected): 25xAA, 10xAB, 20xBA, 55xBB
```{r}
a1 <- c(rep("A", each = 35), rep("B", each = 75))
a2 <- c(rep("A", each = 25), rep("B", each = 10),
        rep("A", each = 20), rep("B", each = 55))
vasarely_data3 <- data.frame(a1,a2)
vasarely(vasarely_data3)
```
AB-deficit(corrected)
```{r}
a1 <- c(rep("A", each = 50), rep("B", each = 60))
a2 <- c(rep("A", each = 25), rep("B", each = 25),
        rep("A", each = 20), rep("B", each = 40))
vasarely_data4 <- data.frame(a1,a2)
vasarely(vasarely_data4)
```

