---
title: "Vasarely Tests"
author: "Alexandra Banach 649005"
date: "29 Juni 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/limes/Documents/Semester6/Bachelorarbeit/vasarely/R")
library("vasarely")
```

load testdata (without column X) and test plot function
```{r}
testdata <- as.data.frame(read.csv("testdata5"))
```
test grey value parameter with false input
```{r}
library(vasarely)
vasarely(testdata, testdata)
```
test data with more than two columns
```{r}
testdata3 <- as.data.frame(read.csv("testdata"))
vasarely(testdata3,blues9)
```
test data with less than two columns
```{r}
testdata4 <- as.data.frame(read.csv("testdata_new"))
testdata4$allel2 <- NULL
vasarely(testdata4, blues9)
```
test data with grey values
```{r}
vasarely(testdata, blues9)
vasarely(testdata)
```
test data with numbers
```{r}
 
a <- rep(c(1:10), each = 10)
b <- sample(c(1:10), 100, replace = TRUE)
data2 <- data.frame(a, b)
vasarely(data2)
```

official example

```{r }
a3 <- c(rep("A", each = 25), rep("B", each = 75))
a4 <- c(rep("A", each = 50), rep("B", each = 50))
data3 <- data.frame(a3, a4)
vasarely(data3)
```

Check if package was successfully installed
```{r}
"vasarely" %in% rownames(installed.packages())
```
Testcase upper/ lower color value: not a number
```{r}
vasarely(data3, upper_color_value = a)
vasarely(data3, upper_color_value = "2")
vasarely(data3, lower_color_value = a)
vasarely(data3, lower_color_value = "2")
```
Testcase upper/ lower color value: is a vector
```{r}
vasarely(data3, upper_color_value = c(0:1))
vasarely(data3, lower_color_value = c(0:1))
```
Testcase upper/ lower color value: only upper value chosen
```{r}
vasarely(data3, upper_color_value = 0.9)
```
Testcase upper/ lower color value: only lower value chosen
```{r}
vasarely(data3, lower_color_value = 0.1)
```
Testcase upper/ lower color value: both values chosen right
```{r}
vasarely(data3, lower_color_value = 0.1, upper_color_value = 0.9)
```
Testcase upper/ lower color value: value > 1
```{r}
vasarely(data3, lower_color_value = 1.1)
vasarely(data3, upper_color_value = 1.1)
```
Testcase upper/ lower color value: value < 0
```{r}
vasarely(data3, lower_color_value = -0.1)
vasarely(data3, upper_color_value = -0.1)
```
Testcase upper/ lower color value: lower color value bigger than upper color value
```{r}
vasarely(data3, lower_color_value = 1, upper_color_value = 0)
```
Testcase upper/ lower color value: 
lower color value does not correspond with prob. values
for testdata: 
min expected prob: 0.140625 , min real prob: 0.25, 
max expected prob: 0.390625 , max expected prob: 0.5
```{r}
vasarely(data3, lower_color_value = 0.15, upper_color_value = 0.9)
vasarely(data3, lower_color_value = 0.3, upper_color_value = 0.9)
```
Testcase upper/ lower color value: upper color value does not correspond with prob. values
```{r}
vasarely(data3, lower_color_value = 0.1, upper_color_value = 0.3)
vasarely(data3, lower_color_value = 0.1, upper_color_value = 0.45)
```
